Smelt recapture analysis - clean version

### 2024-09-06 recaptureanalysis/recapsclean.Rmd
Better recapture analyses

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
library(lme4)
library(lmerTest)
library(effects)
library(MuMIn)
library(DT)
load("recaptureanalysis/Recaps2.RData")

@@

>>>>

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
library(lme4)
library(lmerTest)
library(effects)
library(MuMIn)
library(DT)
library(deltamapr)
load("recaptureanalysis/Recaps2.RData")

@@

## Recaptures in the North Delta Arc

Katie was wondering if we could say whether release type impacted number of fish caught in the North Delta Arc.

First we have to figure out what counts as the "north delta arc"

I'm going to say it is the EDSM "Cache/liberty", "Lower Sacramento" and "Sac DWSC",
Suisun Bayk/Marsh" and "Western Delta" strata

```{r}
ggplot()+
  geom_sf(data = R_EDSM_Strata_17P3, aes(fill = Stratum))+
  geom_sf(data = WW_Delta)+
  coord_sf(ylim = c(37.8, 38.5), xlim = c(-122.2, -121.4), crs = 4326)

```
```{r}
#filter out the north delta arc and attach it to the recap data
NorthDeltaArc = filter(R_EDSM_Strata_17P3, Stratum %in% c("Cache Slough/Liberty Island",
                                                         "Lower Sacramento",
                                                         "Suisun Bay/Marsh",
                                                         "Western Delta",
                                                         "Sac Deep Water Shipping Channel")) %>%
  mutate(NorthDeltaArc = TRUE) %>%
  select(Stratum, NorthDeltaArc)

recapND = st_as_sf(recaps3, coords = c("Longitude", "Latitude"), crs = 4326) %>%
  st_transform(crs = st_crs(NorthDeltaArc)) %>%
  st_join(NorthDeltaArc) %>%
  st_drop_geometry() %>%
  mutate(NorthDeltaArc = case_when(NorthDeltaArc ~ 1,
                                   TRUE ~ 0))

NDtest = glm(NorthDeltaArc ~ Type2 + BroodYear, data = recapND, family = "binomial")

summary(NDtest)
```

Huh, not useful.

```{r}
ggplot(recapND, aes(x = Type2, fill = as.factor(NorthDeltaArc)))+ geom_bar()

ggplot(filter(recapND, Type2 != "Unknown", Type2 != "Wild/unmarked"),
              aes(x = Type2, fill = as.factor(NorthDeltaArc)))+ geom_bar(position = "fill")

```
now try without the wild fish

recapND2 = filter(recapND, Type2 != "Unknown", Type2 != "Wild/unmarked") %>%
  mutate(Type3 = case_when(str_detect(Type2, "Hard") ~ "Hard",
                           TRUE ~ "Soft"))

NDtest2 = glm(NorthDeltaArc ~ Type3 + BroodYear, 
              data = recapND2, family = "binomial")

summary(NDtest2)
